formula1

### 2019-12-23 inst/formula1.Rmd
typo

m <- maxp(L2017)
ox <- rank(-points)
oy <- rank(-m)
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,25),ylim=c(0,25),pch=16,
xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE) # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[ox[i]],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

>>>>

m <- maxp(L2017)
ox <- rank(-points)
oy <- rank(-m)
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,25),ylim=c(0,25),pch=16,
xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE) # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[oy[i]],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```
